---
title: "Plot"
output: html_document
---
```{r}
library(h2o)
h2o.init()
```
#Standard Coef. Magnitudes for GLM model (whole dataset)
#All Features 
```{r}
Co_reg_glm_all<-data.frame(
feature = M_reg_glm_all@model$coefficients_table$names,
Cosd_coefficient = M_reg_glm_all@model$coefficients_table$standardized_coefficients,
group = c("A",rep("iRNA",156),rep("WHISTLE_genomic",35),rep("Regulators",17)),
PN=rep("Positive",209)
)

Co_reg_glm_all<- Co_reg_glm_all[Co_reg_glm_all$feature != "Intercept",]
Co_reg_glm_all$PN[which(Co_reg_glm_all$Cosd_coefficient<0)] <- "Negative"
Co_reg_glm_all$AB = abs(Co_reg_glm_all$Cosd_coefficient)

a <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="iRNA")
a <- a[order(a$AB,decreasing=TRUE),]
b <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="WHISTLE_genomic")
b <- b[order(b$AB,decreasing=TRUE),]
c <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="Regulators")
c <- c[order(c$AB,decreasing=TRUE),]
D = rbind(a,b,c)
D$PN <- as.factor(D$PN)
D$group<-factor (D$group,order=TRUE,levels=c ("iRNA","WHISTLE_genomic","Regulators"))
plot_Co_reg_glm_all_whole_graph<- ggplot(D, aes(x=reorder(feature,AB), y= AB,fill=PN)) + geom_bar(stat='identity', position=position_dodge())+
  theme(axis.text.x = element_text(face="bold"),plot.title = element_text(hjust = 0.5,face="bold"))+
  facet_grid(group~ .,scales = "free", space = "free")+coord_flip()+
  labs(title="Standard Coef. Magnitudes for GLM model (whole dataset)", x="Fetures", y="Strandard Coefficient")

```
# Standard Coef. Magnitudes for GLM model (whole dataset)
#Features (Top 7 in each feature group)
```{r}
Co_reg_glm_all<-data.frame(
feature = M_reg_glm_all@model$coefficients_table$names,
Cosd_coefficient = M_reg_glm_all@model$coefficients_table$standardized_coefficients,
group = c("A",rep("iRNA",156),rep("WHISTLE_genomic",35),rep("Regulators",17)),
PN=rep("Positive",209)
)

Co_reg_glm_all<- Co_reg_glm_all[Co_reg_glm_all$feature != "Intercept",]
Co_reg_glm_all$PN[which(Co_reg_glm_all$Cosd_coefficient<0)] <- "Negative"
Co_reg_glm_all$AB = abs(Co_reg_glm_all$Cosd_coefficient)

a <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="iRNA")
a <- a[order(a$AB,decreasing=TRUE),][1:7,]
b <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="WHISTLE_genomic")
b <- b[order(b$AB,decreasing=TRUE),][1:7,]
c <- subset(Co_reg_glm_all,Co_reg_glm_all$group=="Regulators")
c <- c[order(c$AB,decreasing=TRUE),][1:7,]
D = rbind(a,b,c)
D$PN <- as.factor(D$PN)
D$group<-factor (D$group,order=TRUE,levels=c ("iRNA","WHISTLE_genomic","Regulators"))
plot_Co_reg_glm_all <- ggplot(D, aes(x=reorder(feature,AB), y= AB,fill=PN)) + geom_bar(stat='identity', position=position_dodge())+
  theme(axis.text.x = element_text(face="bold"),plot.title = element_text(hjust = 0.5,face="bold"))+
  facet_grid(group~ .,scales = "free")+coord_flip()+
  labs(title="Standard Coef. Magnitudes for GLM model (whole dataset)", x="Features (Top 7 in each feature group)", y="Strandard Coefficient")
```
#Standard Coef. Magnitudes for GLM model (subdataset)
#All Features
```{r}
Co_reg_glm_all_no0<-data.frame(
feature = M_reg_glm_all_no0@model$coefficients_table$names,
Cosd_coefficient = M_reg_glm_all_no0@model$coefficients_table$standardized_coefficients,
group = c("A",rep("iRNA",156),rep("WHISTLE_genomic",35),rep("Regulators",17)),
PN=rep("Positive",209)
)

Co_reg_glm_all_no0<- Co_reg_glm_all_no0[Co_reg_glm_all_no0$feature != "Intercept",]
Co_reg_glm_all_no0$PN[which(Co_reg_glm_all_no0$Cosd_coefficient<0)] <- "Negative"
Co_reg_glm_all_no0$AB = abs(Co_reg_glm_all_no0$Cosd_coefficient)

a <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="iRNA")
a <- a[order(a$AB,decreasing=TRUE),]
b <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="WHISTLE_genomic")
b <- b[order(b$AB,decreasing=TRUE),]
c <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="Regulators")
c <- c[order(c$AB,decreasing=TRUE),]
D = rbind(a,b,c)
D$PN <- as.factor(D$PN)
D$group<-factor (D$group,order=TRUE,levels=c ("iRNA","WHISTLE_genomic","Regulators"))
plot_Co_reg_glm_all_whole_graph <- ggplot(D, aes(x=reorder(feature,AB), y= AB,fill=PN)) + geom_bar(stat='identity', position=position_dodge())+
  theme(axis.text.x = element_text(face="bold"),plot.title = element_text(hjust = 0.5,face="bold"))+
  facet_grid(group~ .,scales = "free", space = "free")+coord_flip()+
  labs(title="Standard Coef. Magnitudes for GLM model (subdataset)", x="Features", y="Strandard Coefficient")
```
# Standard Coef. Magnitudes for GLM model (subdataset)
# Features (Top 7 in each feature group)
```{r}
Co_reg_glm_all_no0<-data.frame(
feature = M_reg_glm_all_no0@model$coefficients_table$names,
Cosd_coefficient = M_reg_glm_all_no0@model$coefficients_table$standardized_coefficients,
group = c("A",rep("iRNA",156),rep("WHISTLE_genomic",35),rep("Regulators",17)),
PN=rep("Positive",209)
)

Co_reg_glm_all_no0<- Co_reg_glm_all_no0[Co_reg_glm_all_no0$feature != "Intercept",]
Co_reg_glm_all_no0$PN[which(Co_reg_glm_all_no0$Cosd_coefficient<0)] <- "Negative"
Co_reg_glm_all_no0$AB = abs(Co_reg_glm_all_no0$Cosd_coefficient)

a <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="iRNA")
a <- a[order(a$AB,decreasing=TRUE),][1:7,]
b <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="WHISTLE_genomic")
b <- b[order(b$AB,decreasing=TRUE),][1:7,]
c <- subset(Co_reg_glm_all_no0,Co_reg_glm_all_no0$group=="Regulators")
c <- c[order(c$AB,decreasing=TRUE),][1:7,]
D = rbind(a,b,c)
D$PN <- as.factor(D$PN)
D$group<-factor (D$group,order=TRUE,levels=c ("iRNA","WHISTLE_genomic","Regulators"))
plot_Co_reg_glm_all_no0 <- ggplot(D, aes(x=reorder(feature,AB), y= AB,fill=PN)) + geom_bar(stat='identity', position=position_dodge())+
  theme(axis.text.x = element_text(face="bold"),plot.title = element_text(hjust = 0.5,face="bold"))+
  facet_grid(group~ .,scales = "free")+coord_flip()+
  labs(title="Standard Coef. Magnitudes for GLM model (subdataset)", x="Features (Top 7 in each feature group)", y="Strandard Coefficient")
```
# Organize the two Standard Coef. Magnitudes figures
```{r}
library(ggplot2)
library(patchwork)

Plot_co <- plot_Co_reg_glm_all+plot_Co_reg_glm_all_no0
Plot_co + plot_annotation(
  title = 'Figure 1.Standard Coef. Magnitudes for two GLM regression models',
  caption = '*Subdataset include the sites that at least methylated in one sample (among 40 samples)',
  tag_levels = 'A')


```
# Organize the figrues relate to feature importance
```{r}
library(ggplot2)
library(patchwork)

Plot_rf <- plot_cla_rf_irna+plot_cla_rf_irna_whistle+plot_cla_rf_all+plot_reg_rf_irna+plot_reg_rf_irna_whistle+plot_reg_rf_all
Plot_rf + plot_annotation(
  title = 'Figure 2.Feature importance for Random Forest Classification and Poisson Regression models',
  caption = '*',
  tag_levels = 'A')

(plot_cla_rf_irna+plot_reg_rf_irna)/(plot_cla_rf_irna_whistle+plot_reg_rf_irna_whistle)/(plot_cla_rf_all+plot_reg_rf_all)+plot_annotation(
  title = 'Figure 2.Feature importance for Random Forest Classification and Poisson Regression models',
  caption = '*',
  tag_levels = 'A')
```

# Sequence logo (bits & probability)
```{r}
library(BSgenome.Hsapiens.UCSC.hg19)
dss <- DNAStringSet(Views(Hsapiens, m6Ads@rowRanges+2))
dss_df <- data.frame(seq=as.character(dss), Y=rowSums(assay(m6Ads)))
Seqrep <- rep(dss_df$seq,dss_df$Y)
glogo1 <- ggseqlogo::ggseqlogo(Seqrep, method="bits")+annotate('rect', xmin = 2.5, xmax = 3.5, ymin = -0.05, ymax = 2.1, alpha = .1, col='black', fill='yellow')
glogo2 <- ggseqlogo::ggseqlogo(Seqrep, method="probability")+annotate('rect', xmin = 2.5, xmax = 3.5, ymin = -0.05, ymax = 1.05, alpha = .1, col='black', fill='yellow')
```

#the predicted map (RF all)

```{r}
pred_cla_rf_all<- pred_cla_rf_all[order(as.numeric(rownames(pred_cla_rf_all))),,drop=FALSE]
pred_reg_rf_all<- pred_reg_rf_all[order(as.numeric(rownames(pred_reg_rf_all))),,drop=FALSE]
pred_rf_all <- cbind(pred_cla_rf_all,pred_reg_rf_all$predict)
pred_rf_all <- cbind(pred_rf_all,pred_reg_rf_all$predict/40)
names(pred_rf_all)[names(pred_rf_all) == 'pred_reg_rf_all$predict'] <- 'Poisson rate'
names(pred_rf_all)[names(pred_rf_all) == 'pred_reg_rf_all$predict/40'] <- 'Normalized Poisson rate'
pred_rf_all$site <- 1:1624625 

df <- data.frame(seqnames=seqnames(m6Ads),
starts=start(m6Ads)-1,
ends=end(m6Ads),
strands=strand(m6Ads))

library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(Homo.sapiens)
txdb <- TxDb.Hsapiens.UCSC.hg19.knownGene
ebt <- exonsBy(txdb, by="gene")

#transcriptsByGene = transcriptsBy(TxDb.Hsapiens.UCSC.hg19.knownGene, by="gene")
overlaps = findOverlaps(m6Ads@rowRanges, ebt)
overlaps<- data.frame(site=queryHits(overlaps), gene_id=subjectHits(overlaps))

library(dplyr)
map <- left_join(pred_rf_all,overlaps,by="site")
dup <- data.frame(table(map$site))
dup <- subset(dup,dup$Freq>1)
for(i in 1:nrow(dup)){    # Forget to use apply funciton instead of for loop (my fault!)
  row_number <- which(map$site==dup$Var1[i])
  multiple<-map[row_number,]
  map <- map[-row_number,]
  multiple$gene_id<- paste(multiple$gene_id,collapse=",")
  multiple <- multiple[1,]
  map <- rbind(map,multiple)
}

MAP <- map[order(map$site,decreasing=FALSE),]
setwd("~/pred")
write.table(MAP, file="MAP.csv",sep = ",")
map <- read.csv("MAP.csv",head=FALSE)
```




```{r}
library(patchwork)
logos <- (scatter+scatter2)/(glogo1+glogo2)+plot_annotation(
  caption = '*',
  tag_levels = 'A')
```


```{r}
remove(df_reg_rf_all_Y)
remove(pred_reg_rf_all)

## dot plot regression(log)

pred_reg_rf_all<- read.csv("pred_reg_rf_all.csv")
pred_reg_rf_all$log_predict <- log(pred_reg_rf_all$predict+1) # add 1 because many 0 in the datasets
pred_reg_rf_all$log_Y <- log(pred_reg_rf_all$Y+1)


dot_plot_regression<- ggplot(data = pred_reg_rf_all,aes(x=log_predict,y=log_Y,colour=log_Y))+
                      geom_point(size = 1, alpha = 0.1)+ 
                      xlab("ln(Poisson regression fit+1)")+ylab("   ln(real sample count+1)  ")+
                      labs(fill = "   ln(real sample count+1)  ")+
                      guides(fill=guide_legend(title="   ln(real sample count+1)  "))+
                      expand_limits(x=c(0,log(40+1), y=c(0, log(40+1))))+
                      scale_color_gradientn(colours = rainbow(5))+
                      theme(legend.title.align = 0,legend.title = element_text(face = "italic", size = 10))+
                      theme(axis.line.x=element_blank())
                      #scale_x_discrete(expand = waiver())+ 
                      #scale_y_discrete(expand = waiver())
dot_plot_regression[["labels"]][["colour"]] <- "   ln(real sample count+1)  "

                                    
dot_plot_regression                                
                                    
# the y axs histogram                                    
pred_reg_rf_all_logY_group <- cut(pred_reg_rf_all$log_Y, breaks = seq(from=0, to=log(40+1), by=0.01),right = FALSE)
df_reg_rf_all_logY <- data.frame(table(pred_reg_rf_all_logY_group))
df_reg_rf_all_logY$axs <- (1:371)/100-0.005
                                    
df_reg_rf_all_logY$log_count <- log(df_reg_rf_all_logY$Freq+1)   
```

```{r}  
p1_l <-  ggplot(df_reg_rf_all_logY, aes(x=axs,y=log_count)) + 
       xlab(NULL)+ylab("ln(count+1)")+
       geom_col(aes(x = axs),width=0.04, fill = rainbow(length(df_reg_rf_all_logY$axs)))+
       theme_classic()+
       theme(axis.ticks.y  = element_blank())+
       scale_y_reverse(expand = c(0,0))+
   scale_y_reverse()+
       coord_flip()+
       scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3),expand = c(0,0))+
   scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3))+
       theme(axis.line.x=element_blank())+
       theme(axis.ticks.y = element_line())
p1_l 

```

```{r} 
                                    
# the x axs histogram                                  
pred_reg_rf_all_logpredict_group <- cut(pred_reg_rf_all$log_predict, breaks = seq(from=0, to=log(40+1), by=0.1),right = FALSE)
df_reg_rf_all_logpredict <- data.frame(table(pred_reg_rf_all_logpredict_group))
df_reg_rf_all_logpredict$axs <- (1:37)/10-0.05
df_reg_rf_all_logpredict$log_count <- log(df_reg_rf_all_logpredict$Freq+1) 
                                    

```
```{r} 
p1_u <- ggplot(df_reg_rf_all_logpredict, aes(x=axs,y=log_count)) + 
      xlab(NULL)+ylab("ln(count+1)")+
     geom_bar(aes(fill = axs), stat = "identity") +
     theme_classic()+
     labs(fill = "ln(Poisson regression fit+1)")+ 
     scale_fill_gradient(low ="purple" , high ="yellow" , na.value = NA)  +
     theme(legend.title.align = 0,
      legend.title = element_text(
      face = "italic", 
      size = 10))+
      scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3),expand = waiver())+  
      scale_y_reverse()+
      coord_cartesian(expand = FALSE) +
     theme(axis.line.y=element_blank())  
p1_u                         
                            
```
# Organize the two Standard Coef. Magnitudes figures
```{r}
library(dplyr)
co_1 <- ggpubr::ggarrange(p1_l,dot_plot_regression, NULL, p1_u, 
          ncol = 2, nrow = 2,  align = "hv", 
          widths = c(1, 2), heights = c(2, 1))
co_1
```


```{r}
## dot plot classification(log)
prediciton_cla_rf_all3$multiply<- prediciton_cla_rf_all3$p1*40
prediciton_cla_rf_all3$log_predict <- log(prediciton_cla_rf_all3$multiply+1)
prediciton_cla_rf_all3$log_Y <- log(prediciton_cla_rf_all3$Yor+1) 




dot_plot_classification<- ggplot(data = prediciton_cla_rf_all3,aes(x=log_predict,y=log_Y,colour=log_Y))+
                      geom_point(size = 1, alpha = 0.1)+ 
                      xlab("ln(classification prediction+1)")+ylab("    ln(real sample count+1)    ")+
                      labs(fill = "    ln(real sample count+1)    ")+
                      guides(fill=guide_legend(title="ln(real sample fit+1) "))+
                      expand_limits(x=c(0,log(40+1), y=c(0, log(40+1))))+
                      scale_color_gradientn(colours = rainbow(5))+
                      theme(legend.title.align = 0,legend.title = element_text(face = "italic", size = 10))+
                      theme(axis.line.x=element_blank())

dot_plot_classification[["labels"]][["colour"]] <- "    ln(real sample count+1)    "
                                    
dot_plot_classification                               
                                    
# the y axs histogram                                    
pred_cla_rf_all_logY_group <- cut(prediciton_cla_rf_all3$log_Y, breaks = seq(from=0, to=log(40+1), by=0.01),right = FALSE)
df_cla_rf_all_logY <- data.frame(table(pred_cla_rf_all_logY_group))
df_cla_rf_all_logY$axs <- (1:371)/100-0.005
                                    
df_cla_rf_all_logY$log_count <- log(df_cla_rf_all_logY$Freq+1)  

```

```{r}  
p2_l <-  ggplot(df_cla_rf_all_logY, aes(x=axs,y=log_count)) + 
       xlab(NULL)+ylab("ln(count+1)")+  #count
       geom_col(aes(x = axs),width=0.04, fill = rainbow(length(df_cla_rf_all_logY$axs)))+
       theme_classic()+
       theme(axis.ticks.y  = element_blank())+
       scale_y_reverse(expand = c(0,0))+
   scale_y_reverse()+
       coord_flip()+
       scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3),expand = c(0,0))+
   scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3))+
       theme(axis.line.x=element_blank())+
       theme(axis.ticks.y = element_line())
p2_l 

```

```{r} 
                                    
# the x axs histogram                                  
pred_cla_rf_all_logpredict_group <- cut(prediciton_cla_rf_all3$log_predict, breaks = seq(from=0, to=log(40+1), by=0.1),right = FALSE)
df_cla_rf_all_logpredict <- data.frame(table(pred_cla_rf_all_logpredict_group))
df_cla_rf_all_logpredict$axs <- (1:37)/10-0.05
df_cla_rf_all_logpredict$log_count <- log(df_cla_rf_all_logpredict$Freq+1) 
                                    

```
```{r} 
p2_u <- ggplot(df_cla_rf_all_logpredict, aes(x=axs,y=log_count)) + 
      xlab(NULL)+ylab("ln(count+1)")+
     geom_bar(aes(fill = axs), stat = "identity") +
     theme_classic()+
     labs(fill = "ln(classification predict+1)")+ 
     scale_fill_gradient(low ="purple" , high ="yellow" , na.value = NA)  +
     theme(legend.title.align = 0,
      legend.title = element_text(
      face = "italic", 
      size = 10))+
      scale_x_discrete(position = "top",labels = abbreviate,limits=c(0,1,2,3),expand = waiver())+  
      scale_y_reverse()+
      coord_cartesian(expand = FALSE) +
     theme(axis.line.y=element_blank())  
p2_u                         
                            
```